---
title: "Project proposal"
author: "TROUT1"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(scales)
```

## 1. Introduction

In this project we will explore how factors such as: Location, House type, Area and Number of bathrooms influence the price of properties in London. We will then use this information to investigate how the price of housing in London varies with the number of bathrooms.

[Here is the dataset we plan on using.](https://www.kaggle.com/arnavkulkarni/housing-prices-in-london)

This dataset contains 11 variables. Although a couple of these variables are redundant (like the '#' variable, the 'Property Name' variable and the 'Postal Code' variable). 

The variables in this dataset are: '#', 'Property Name', 'Price', 'House Type', 'Area in sq ft', 'No. of Bedrooms', 'No. of Bathrooms', 'No. of Receptions', 'Location', 'City/County', 'Postal Code'.
All of these are self explanatory except '#' which is an id for each listing.

Each row in this dataset is a listing for a property.

From the Metadata on the dataset's kaggle page the data was obtained through Web Scraping.

## 2. Data

```{r load-dataset, message = FALSE}
London <- read_csv("../data/London.csv")
glimpse(London)
```

## 3. Data analysis plan

The final goal of our project is to answer: "Does the number of bathrooms affect the price of a property in London?"

Response factor: The price of the property (London$Price)
Explanatory factor: The number of bathroom in each factor (London$No. of Bathrooms)

Here is a glimpse of the relation between those two factors
```{r simple analysis-number of bathroom vs price}
pound_in_M <- label_dollar(
  prefix = "£",
  suffix = "M",
  big.mark = ",",
  decimal.mark = "."
)
London%>%
  mutate( 
    price_in_M = Price/1000000
  )%>%  #We reduce the number of price into M(e.g.:£1000000->£1M)
  ggplot(aes(x = `No. of Bathrooms`, y = price_in_M))+
  geom_point()+
  geom_smooth(method = "lm")+
  scale_y_continuous(labels = pound_in_M)+
  labs(
    title = "Price vs No. of Bathroom plot, with regression line",
    subtitle = "For properties in London",
    x = "Number of bathrooms",
    y = "Price of property"
  )
```

The answer seems to be "Yes", since the regression line shows a slope. But there are still a lot of problems with this plot:
1. The slope doesn't seem to fit the data welll
2. There are too many confounding variables, this plot could be showing area per sq foot increases the price, and number of bathrooms is correlated with a greater area per sq foot. To understand the influence the number of bathrooms has on price we will have to investigate further.

We will solve these problems in the actual project.

If we really want to get the answer that "the number of bathrooms do affect the price of the property", we need to do those:
1. Remove the confounding variables (This will be the majority of the work we are going to do)
2. Show that there is a strong relationship between the number of bathrooms and the price of the property

